\documentclass[letterpaper,10pt]{article}
\usepackage[left=0.6in, right=0.6in, top=0.8in, bottom=0.8in]{geometry}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue]{hyperref}

% Customisations for bold section titles with lines
\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1}
% \setlist[itemize]{noitemsep, topsep=0pt}
\setlist[itemize]{nosep, topsep=0pt, leftmargin=1.5em}

% Header Styling
\pagestyle{empty}

% Command for section titles with a horizontal line
\newcommand{\sectionline}[1]{%
    \vspace{0.7em}%
    \textbf{\large #1} \vspace{-2.0em}\\%
    
    \rule{\textwidth}{0.5pt}%
    \vspace{0.25em}%
}

\begin{document}

% Header

    {\huge \textbf{Kaushal Jha}}\\
        \vspace{2pt}
    Indian Institute of Technology Mandi \\
    \vspace{2pt}
    Himachal Pradesh, India, 175005\\
    \vspace{2pt}
    Email: \href{mailto:s23025@students.iitmandi.ac.in}{s23025@students.iitmandi.ac.in} $\mid$ \href{kaushal892jha@gmail.com}{kaushal892jha@gmail.com}\\
    \vspace{2pt}
    LinkedIn: \href{https://www.linkedin.com/in/kaushal-jha892/}{ linkedin.com/in/kaushal-jha892/}\\
    \vspace{2pt}
    GitHub: \href{ https://github.com/WaRxChaMpioN/SciML_ass_Kaushal.git}{github.com/WaRxChaMpioN}

\vspace{2pt}
% \sectionline{PROFILE}
% Motivated M.Tech (Research) student specialising in Computational Mechanics and Radiative Heat Transfer, aiming to pursue PhD research in fluid–thermal interaction in porous media or solar energy systems. Passionate about advancing simulation-based approaches in energy systems, focusing on accurate thermal modelling, efficiency, and sustainability.
% \textbf{Profile:}  
%     \vspace{2pt}
% Computational mechanics researcher with hands-on experience in porous media modelling, multiphysics simulation, and solver development using Ansys Fluent, OpenFOAM, C++, and Python. Basic machine learning (PyTorch \& Tensorflow Flow) knowledge with a growing interest in integrating data-driven techniques into physical modelling. Strong academic foundation in mechanical engineering with a deep interest in multiphase transport phenomena and simulation-driven research.




% Education Section
\sectionline{EDUCATION}
% \\
\begin{itemize}
    \item \textbf{Indian Institute Of Technology Mandi, Himachal Pradesh, India} \hfill August 2023 -- Present\\
    \textit{M.Tech (Research) - Computational Mechanics}
    \begin{itemize}[nosep]
        \item CGPA: $8/10$
        \item Research Area: CFD, Radiative Heat Transfer, Porous Media, Collimated Beam
        \item Supervisor: Dr. Pradeep Kumar, Associate Professor
        \item Coursework: Advanced analytical Techniques, Introduction to Turbulence and its modelling, Thermodynamics of energy systems, Combustion Technology, Multiphase Flows, Numerical Methods, scientific Machine Learning for engineers, and more
    \end{itemize}
    \vspace{0.5em}
    \item \textbf{Dr A P J Abdul Kalam Technical University, Uttar Pradesh, India} \hfill  June 2023\\
    \textit{B.Tech - Mechanical Engineering}
    \begin{itemize}[nosep]
        \item CGPA: $7.51/10$
        \item Coursework: Engineering Mechanics, Fluid Mechanics, Thermodynamics, Heat Transfer, and more
        \item Thesis: Design and Development of Portable Spot Welding Machine for Small-Scale Industries
    \end{itemize}
    \vspace{0.5em}
    \item \textbf{Senior Secondary (CBSE)}— 82.8 \%  \hfill  May 2019

\end{itemize}

% Academic Projects
\sectionline{ACADEMIC / RESEARCH PROJECTS }
% \textbf{Investigating role of radiation in the porous medium for concentrated solar applications ( Research Work, M.Tech (Research) )} \hfill May 2024 -- On-going\\
% \textit{Guide: Dr. Pradeep Kumar, Associate Professor }
% \begin{itemize}[nosep]
%     \item Using pore-scale simulations, developing a detailed numerical framework to study heat transfer and fluid flow in a volumetric solar receiver (VSR) system.
%     \item Worked on Monte Carlo radiation modelling in ANSYS Fluent to capture inter-pore radiative heat transfer in an ordered alumina porous medium.
%     \item Calculated effective radiative properties (e.g., conductivity, absorption coefficient); and found radiation effects significantly increase at higher irradiation, equivalent to the porous media's bulk conductance.
%     \item Worked with Ansys for pore-scale simulations, OpenFOAM for modelling Darcy–Forchheimer equation in porous medium, ICEM-CFD, spacclaim, MSLattice, etc 
% \end{itemize}
% \vspace{0.5em}
% \textbf{Design and Development of Portable Spot Welding Machine (Major Project, B.Tech)} \hfill Dec 2022 -- May 2023\\
% \textit{Mentor: Bishub Choudhary, Ph.D, Assistant Professor}
% \begin{itemize}[nosep]
%     \item Designed a portable, low-cost resistance spot welding machine for small-scale industries, utilising recycled materials and keeping the total cost under {\$}60.
%     \item Used Fusion 360 for design, integrating a 1500-amp transformer and an adjustable handle for one-handed operation and mobility. Ensured ease of use and portability for diverse industrial applications.
%     \item Published a review article (chapter) and a conference paper at the end of the project.
% \end{itemize}
% \vspace{0.5em}
% \textbf{Air Purification System (Minor Project, B.Tech)} \hfill Sep 2021 -- Jan 2022\\
% \textit{Mentor: Dr. Shailesh Singh, Professor}
% \begin{itemize}[nosep]
%     \item Developed an air purification system with three stages: a HEPA filter for suction, an electrostatic precipitator to remove PM2.5, and a carbon filter to eliminate ozone and microorganisms, ensuring safe air for breathing.
%     \item Integrated a flyback transformer to achieve 20,000 volts for the electrostatic precipitator, with a custom-built ESP absorber for efficient performance.
% \end{itemize}
% \textbf{\large Research Projects} 
\begin{itemize}[leftmargin=*]

\item \textbf{Tunneling Through the Fog for Long-Distance Visibility} (M.Tech Research) 
  \hfill April 2025 -- Present \\
  \textit{Guide: Dr. Pradeep Kumar, Associate Professor}
  \begin{itemize}[noitemsep,topsep=0pt]
    \item Analysed complex refractive indices of ice and water across microwave, infrared, and visible spectra.
    \item Developed a simulation framework for laser heating of fog (water droplets and ice crystals) using Volume-of-Fluids and Monte Carlo ray-tracing methods.
    \item Prepared technical poster, presentation, and report highlighting future research directions.
    \item \textbf{Key Skills:} Fog Modelling, Monte Carlo Ray Tracing, Volume-of-Fluids (Ansys Fluent), Optical Properties, Python, Tecplot.
  \end{itemize}
    \vspace{0.5em}

\item \textbf{Radiation in Porous Medium for Solar Energy Applications} (M.Tech Research)
  \hfill April 2024 -- Present \\
  \textit{Guide: Dr. Pradeep Kumar, Associate Professor }
  \begin{itemize}[noitemsep,topsep=0pt]
    \item Developed a framework to simulate radiative and convective transport in a volumetric solar receiver (VSR).
    \item Estimated effective radiative and thermal properties via Monte Carlo ray tracing in ANSYS Fluent.
    \item Modelled porous media using Darcy–Forchheimer equation in OpenFOAM.
    \item Simulated multi-region fluid flow with custom radiation boundary conditions at the interface.
    \item Achieved comparable results to pore-scale simulation using a complete fluid-domain approximation, significantly reducing computational cost.
    \item \textbf{Key Skills:} Radiative heat transfer, Monte Carlo Ray Tracing, Porous media modelling, OpenFOAM, ANSYS Fluent, SolidWorks, ICEM-CFD, SpaceClaim, Ansys Meshing, C/C++, Python, Matlab, Tecplot.
  \end{itemize}
      \vspace{0.5em}

\item \textbf{Portable Spot Welding Machine} (B.Tech Major Project) \hfill Dec 2022 -- May 2023\\
  \textit{Mentor: Bishub Choudhary, Ph.D, Assistant Professor}
  \begin{itemize}[noitemsep,topsep=0pt]
    \item Designed a low-cost resistance spot welding machine (\textless\$60 budget).
    \item Used Fusion 360 for 3D design; integrated a 1500A transformer.
    \item Published 1 conference paper, 1 book chapter, and a Design Patent (filed, under Review).
    \item \textbf{Key Skills:} Product Design, Fusion 360, Resistance Welding, Prototyping, Technical Writing.
  \end{itemize}
      \vspace{0.5em}

\item \textbf{Air Purification System} (Minor Project, B.Tech) \hfill Sep 2021 -- Jan 2022\\
  \textit{Mentor: Dr. Shailesh Singh, Professor}
  \begin{itemize}[noitemsep,topsep=0pt]
    \item Built a three-stage system (HEPA + electrostatic precipitator + carbon filter) to remove PM2.5 and harmful gases.
    \item Designed a high-voltage ESP module powered by a flyback transformer for enhanced particle capture.
    \item \textbf{Key Skills:} Air Quality Systems, ESP Design, High-Voltage Circuits, Prototype Development.
  \end{itemize}
      \vspace{0.5em}

\end{itemize}
% Work/Internship Experience
\sectionline{WORK/INTERNSHIP EXPERIENCE}
\begin{itemize}[leftmargin=*]
    \item \textbf{Aktiv Technologies Pvt. Ltd, Faridabad} \hfill June 2023 -- July 2023\\
        \textit{Intern, Design and Development}
        \begin{itemize}[nosep]
            \item Applied SolidWorks for reverse engineering, creating 3D solid models and 2D manufacturing drafts.
            \item Prepared product catalogues and visualisation materials using CorelDRAW and SolidWorks Visualise.
            \item \textbf{Key Skills:} SolidWorks, Reverse Engineering, 2D Drafting, Product Visualization, CorelDRAW.
        \end{itemize}
    \vspace{0.5em}
    
    \item \textbf{Satyam Auto Components Pvt. Ltd, Gurgaon} \hfill May 2023 -- June 2023\\
        \textit{Graduate Engineer Trainee, Quality Assurance}
        \begin{itemize}[nosep]
            \item Oversaw heavy press-line production of fuel tanks and air filters for two-wheelers and heavy vehicles.
            \item Performed quality assurance for resistance spot welding and stamping operations.
            \item \textbf{Key Skills:} Quality Assurance, Manufacturing Processes, Resistance Welding, Heavy Press Line Operations.
        \end{itemize}
\end{itemize}


% Awards and Achievements
% \newpage
\sectionline{HONORS, AWARDS \& SCHOLARSHIPS}

\begin{itemize}
    \item \textbf{$1^{st}$ place} - poster presentation in 1-Day Symposium on Mechanical and Materials Engineering in IIT Mandi, 2024
    \item \textbf{GATE Qualified } - National level engineering entrance exam, 2023
    \item \textbf{Research Assistantship} (HTRA) - Ministry of Education (MoE), Govt. of India, 2023
    \item \textbf{All India Rank 90} - NCAT, the National Creativity and Aptitude Test (among 23000+ Engineering students), 2020

\end{itemize}
% Conference and Publication Section
\sectionline{PUBLICATIONS}

\begin{itemize}
    \item \textbf{Kaushal Jha}, Surendra Singh Rathore, Balakrishna Mehta, Pradeep Kumar. “Investigating the role of radiation in porous medium for concentrated solar energy applications”. (Journal paper in Review).\\

    \item \textbf{Kaushal Jha}, Surendra Singh Rathore, Balakrishna Mehta, Pradeep Kumar. “Estimation of Effective Thermal Conductivity of Porous Medium
for Volumetric Solar Receiver Cavity-like System”. Submitted to International Heat And Mass Transfer Conference (IHMTC 2025) .\\

    \item \textbf{Kaushal Jha}, Santosh Kumar Tamang, Rajeev Kumar, Bishub Choudhary, "Enhancing Resistance Spot Welding Weld Quality: A Comprehensive Analysis of Influencing Factors and the Role of Modeling and Optimisation," New Materials, Processing and Manufacturability: Fabrication and Processing of Advanced Materials, Chapter 5, Editors: R. Thanigaivelan, Pradeep Kumar Krishnan, Kamalakanta Muduli, Santosh Kumar Tamang, Wiley, \textbf{25 July 2024}. \href{https://doi.org/10.1002/9781394212736.ch5}{https://doi.org/10.1002/9781394212736.ch5}.\\
    \item \textbf{Kaushal Jha}, Akshaj Jumde, Gautam Kumar, Rick Dutta, Krati Hardya, Shailesh Kumar Singh, and Bishub Choudhary. “Design and Development of a Portable Resistance Spot Welding Machine for Small-Scale Industries.” Applied Mechanics and Materials, Trans Tech Publications, Ltd., \textbf{February 5, 2024}. \href{https://doi.org/10.4028/p-xcpkt9}{https://doi.org/10.4028/p-xcpkt9} .

\end{itemize}





\sectionline{CONFERENCE PRESENTATION}
\begin{itemize}
    \item \textbf{Kaushal Jha}, "Design and Development of Portable Resistance Spot Welding Machine for Small Scale Industries," Conference on Advancements in Materials, Manufacturing and Automation (AMMA 2023), Amrita Vishwa Vidyapeetham, 2023.
    
\end{itemize}

% Skills & Competencies
\sectionline{SKILLS }
\begin{itemize}[leftmargin=*]
  \item \textbf{Tools:} OpenFOAM, ANSYS (Fluent, SpaceClaim, ICEM), Fusion 360, SolidWorks
  \item \textbf{Programming:} C, C++, Python, Fortran, MATLAB
  \item \textbf{Platforms:} Windows, Ubuntu 
  % \quad $\mid$ \quad \textbf{Docs:} 
  \item \textbf{Docs:} LaTeX, MS Office
\end{itemize}

% \textbf{Soft Skills:} List of soft skills

\sectionline{REFERENCES}
\begin{itemize}
    \item Dr. Pradeep Kumar, Associate Professor (M.Tech(R) Supervisor), IIT Mandi, Email: \href{pradeepkumar@iitmandi.ac.in}{pradeepkumar@iitmandi.ac.in}
    \item Dr. Butunath Majhy, Assistant Professor, IIT Guwahati, Email: \href{majhybutunath@gmail.com}{majhybutunath@gmail.com}
    \item Dr. Bishub Choudhary, Post-Doc, IISc Bangalore (B.Tech Supervisor), Email: \href{bishub.choudhary73@gmail.com}{bishub.choudhary73@gmail.com}
\end{itemize}

\end{document}
